map_enclosure_sites

### 2023-11-22 smelt_2019_allseasons/Diet 2019.Rmd
Adding biofouling analyses

#sum for taxa abundance among individual fish
taxa_tag<- diet %>% 
  group_by(Location, tlc, Taxa) %>% 
  summarize("count.sum"= sum(Count))

>>>>

#write csv for use in biofouling comparison
write.csv(diet, "smelt_2019_allseasons/data_clean/Diet.proportions.csv", row.names=FALSE)
```

```{r}

#plot at the higher taxonomic level

ggplot(diet, aes(x = Tag, y = Count, fill = Prey.Taxa)) +
  geom_col(position = "fill")+
  facet_wrap(~Location, scales = "free")

ggplot(diet, aes(x = Location, y = Count, fill = Prey.Taxa)) +
  geom_col(position = "fill")

preytaxa = group_by(diet, Prey.Taxa) %>%
  summarize(Count = sum(Count))
rare = filter(preytaxa, Count <=2)

#clean it up a little
library(Polychrome)
pal36 <- palette36.colors(36)
pal36 <- as.vector(t(pal36))

diet = filter(diet, !Prey.Taxa %in% c('empty', "EMPTY", 'plant matter')) %>%
  mutate(Prey.Taxa = case_match(Prey.Taxa, c("Culicidae", "Hemiptera") ~ "Insecta",
                                c("Leydigia sp.", "Alona sp.", "Diaphanosoma sp.", "Eurycercus sp.") ~ "Cladocera",
                                c("Tropocyclops sp.", "Macrocyclops sp.") ~ "Cyclopoida",
                                .default = Prey.Taxa))%>%

  mutate(Preytax = factor(Prey.Taxa, levels = c( "Cyclopoida","Acanthocyclops sp.", "Diacyclops thomasi", "Eucyclops sp.", "Halicyclops sp.",  "Mesocyclops sp.", "Calanoida", "Diaptomidae",
                                                "Eurytemora affinis", "Osphranticum labronectum", "Pseudodiaptomus forbesi", 
                                                "Harpacticoida", "Sinocalanus doerrii","Cladocera",  "Bosmina sp.", 
                                                "Ceriodaphnia sp.", "Chydoridae", "Chydorus sp.",
                                                "Daphnia sp.",  
                                                 "Scapholeberis sp.", "Sida sp.", "Simocephalus sp.",
                                                "Americorophium sp.", "Crangonyx sp.", "Eogammarus confervicolus",
                                                "Gammaridea", "Hyallela azteca", "Mysidacea","Insecta",
                                                 "Chironomidae", "Ostracoda",
                                                "Cumacea", "Fish","Acari", "Bivalvia")))

ggplot(diet, aes(x = Location, y = Count, fill = Preytax)) +
  geom_col(position = "fill")+
  scale_fill_manual(values = pal36, name = "taxa")+
  theme_bw()+
  ylab("Relative Diet Proportion")

ggsave("smelt_2019_allseasons/figures/fishdiet.tiff", device = "tiff", width = 10, height =6)
# 
# To allow for diets of different sized fish to contribute equally, proportion was calculated by taking the abundance of each taxa divided by the total abundance of all taxa per diet and then averaging across individuals from each enclosure.

dietsummary = group_by(diet, Cage.ID, Location, Tag, tlc) %>%
  mutate(stomachsum = sum(Count), proportion = Count/stomachsum)

#huh, it doesn't look like anyone added teh zeros in for the other verson... maybe I won't bother.

```

```{r}
#sum for taxa abundance among individual fish
taxa_tag<- diet %>% 
  group_by(Location, tlc, Taxa) %>% 
  summarize("count.sum"= sum(Count))

### 2023-11-22 smelt_2019_allseasons/Zoop 2019.Rmd
Adding biofouling analyses

#remove 0's
caught <- all[!(all$ind_m3==0),]
biomass = read_csv("zooptaxa.csv")
caught = left_join(caught, biomass) %>%
  mutate(bio_m3 = Mass*ind_m3)

@@

#First to CPUE
ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=ind_m3, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

#now try BPUE
ggplot() +
  geom_bar(position = "fill", stat = "identity", data=caught, aes (x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Biomass of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

@@

ggplot() +
  geom_bar(position = "fill", stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of Macrozoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))
```

>>>>

#remove 0's
caught <- all[!(all$ind_m3==0),]
biomass = read_csv("data/zooptaxa.csv")
caught = left_join(caught, biomass) %>%
  mutate(bio_m3 = Mass*ind_m3)

@@

#First to CPUE
ggplot() +
  geom_bar(stat = "identity", data=caught, aes (x=MD, y=ind_m3, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

#now try BPUE
ggplot() +
  geom_bar(stat = "identity", data=caught, aes (x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Biomass of all Zoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

@@

ggplot() +
  geom_bar( stat = "identity", data=macro, aes (x=MD, y=samplecount, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of Macrozoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))

ggplot() +
  geom_bar( stat = "identity", data=filter(macro, ID != "Cyclopoid copepodid"), aes(x=MD, y=bio_m3, fill=ID), colour="black", width = .5) +
  facet_wrap(~Location, ncol = 1) +
  theme_bw() + 
  scale_fill_manual(values=pal36)+
  labs(x = "Date") +
  labs(y = "Relative Abundance of Macrozoop in Sample")+
  theme(legend.position="right")+
      theme(axis.text = element_text(size = 12),
      axis.title = element_text(size = 12),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 10),
      axis.text.x = element_text(angle = 90))
